\documentclass[a4paper,10pt]{article}
% --- PACKAGES ---
\usepackage[a4paper,margin=0.6in]{geometry} % Set page margins
\usepackage{lmodern} % Use Latin Modern font
\usepackage{hyperref} % Create hyperlinks
\usepackage{xcolor} % Use colors (though not explicit here, good for links)
\usepackage{fontawesome5} % Use icons like phone, email, etc.
\usepackage{enumitem} % For customizing lists like itemize

% --- FONT, SPACING, LINKS ---
\renewcommand{\baselinestretch}{1.05} % Adjust line spacing slightly
\hypersetup{ % Configure hyperlinks
    colorlinks=true, % Enable colored links
    linkcolor=black, % Color for internal links (e.g., toc)
    citecolor=black, % Color for citations
    filecolor=black, % Color for file links
    urlcolor=black,  % Color for URLs (important for email/web links)
    pdfborder={0 0 0}, % Remove border around links (cleaner look)
}
\setlength{\parindent}{0pt} % No indentation for new paragraphs
\setlength{\parskip}{0pt} % No extra space between paragraphs (control manually or with section breaks)

% --- Custom Command for Sections ---
% Defines a consistent style for section headings
% Usage: \sectionheading{Section Title}
\newcommand{\sectionheading}[1]{%
  \addvspace{\medskipamount}% Add vertical space *before* the heading
  {\large\bfseries\MakeUppercase{#1}} % Format the heading text
  \noindent\rule{\linewidth}{0.4pt}% Draw the horizontal rule immediately after text
  \vspace{\smallskipamount}% Add vertical space AFTER the rule, before content
}

% --- Customize itemize spacing for resume ---
\setlist[itemize]{
    label=*,           % Use asterisk as the bullet
    leftmargin=*,      % Natural indentation (adjust if needed, e.g., leftmargin=2em)
    topsep=0pt,        % Space above list - SET TO 0pt
    partopsep=0pt,     % Extra space above if new paragraph
    itemsep=2pt,       % Space between items
    parsep=0pt         % Space between paragraphs within an item
}


% --- DOCUMENT START ---
\begin{document}

% --- HEADER ---
\begin{minipage}[t]{0.55\textwidth}
    \vspace{0pt} % Ensures top alignment
    {\Large\bfseries Nabil Alsaiad}\\[4pt]
    \textit{Game System \& Tool Programmer}\\[4pt]
    Age: 23, Male
\end{minipage}% <--- The '%' prevents a space between minipages
\hfill % Pushes the next minipage to the right
\begin{minipage}[t]{0.4\textwidth}
    \vspace{0pt} % Ensures top alignment
    \raggedleft % Right-align content within this minipage
    \faPhone\ +60-111-174-1088 \\[4pt]
    \faEnvelope\ \href{mailto:hi@assayyaad.pro}{hi@assayyaad.pro} \\[4pt]
    \faGitlab\ \href{https://gitlab.com/Assayyaad}{Assayyaad} \\[4pt]
    \faGithub\ \href{https://github.com/Assayyaad}{Assayyaad} \\[4pt]
    \faLinkedin\ \href{https://linkedin.com/in/Assayyaad}{Assayyaad}
\end{minipage}

% --- Summary ---
\sectionheading{Summary}
Game System \& Tool Programmer specializing in creating solutions to be used by game developers. Experienced in Unity development with 6 years of hands-on experience, proficient in C\# and JavaScript programming, and skilled in developing game systems, tools, and multiplayer experiences. Passionate about open source development and creating efficient, reusable solutions for the game development community.

% --- Education ---
\sectionheading{Education}

\textbf{Self-Taught Developer} \\
All programming and game development skills acquired through YouTube tutorials, online courses, and independent learning. Continuous self-improvement through hands-on practice and community engagement.

% --- Skills ---
\sectionheading{Skills}

\textbf{Programming Languages:} C\# (Expert), JavaScript (Expert), C++, Java, GDScript, Odin, Rust \\
\textbf{Game Development:} Unity (6+ years), Godot, Bevy, raylib, Game Systems Architecture, Tool Development \\
\textbf{Software Development:} Object-Oriented Programming, Functional Programming, Design Patterns, Data Structures, Software Design \\
\textbf{Development Tools:} Visual Studio (6+ years), Visual Studio Code (5+ years), Git (5+ years), GitHub (5+ years), GitKraken (3+ years) \\
\textbf{Core Competencies:} Problem Solving, Code Analysis, Debugging, Software Testing, AI-Assisted Programming \\
\textbf{Soft Skills:} Project Planning (Milanote), Technical Documentation, Team Collaboration

% --- Experiences ---
\sectionheading{Experiences}

\textbf{Team Leading} -- Led development teams in collaborative game projects, coordinating tasks and ensuring project milestones are met \\
\textbf{Game Jamming (Solo \& With a team)} -- Active participant in game jams, creating games under tight deadlines both independently and as part of teams \\
\textbf{Package Publishing} -- Experience in publishing and maintaining game development packages and tools for community use \\
\textbf{Designing/Programming Tools for other developers} -- Specialized in creating development tools and systems that enhance productivity for fellow game developers

% --- Projects ---
\sectionheading{Projects}

% --- Project 1: Unity Advanced System ---
\textbf{Unity Advanced System} \\
\textit{An advanced system to replace Unity's GameObject with a composition based architecture made of Controllers, Systems, and Workers.}
\begin{itemize}[nosep]
    \item Designed and implemented a comprehensive architecture system to improve Unity's default GameObject model.
    \item Created a composition-based framework consisting of Controllers, Systems, and Workers for better code organization.
    \item Developed reusable components that enhance game development workflow and maintainability.
\end{itemize}

\addvspace{\medskipamount} % Add vertical space between projects

% --- Project 2: Simple Timers ---
\textbf{Simple Timers} \\
\textit{A simple library for creating timers in Unity}
\begin{itemize}[nosep]
    \item Developed a lightweight, easy-to-use timer library for Unity developers.
    \item Created intuitive API for common timing operations in game development.
    \item Focused on performance optimization and memory efficiency for production use.
\end{itemize}

\addvspace{\medskipamount} % Add vertical space between projects

% --- Project 3: Chicken Out ---
\textbf{Chicken Out} -- \href{https://assayyaad.itch.io/chicken-out}{Link (Clickable)} \hfill Unity, C\#, Networking, Multiplayer \hfill June 2021 \\
\textit{An online 4 player multiplayer fighting game with rock-paper-scissors guns and powerups}
\begin{itemize}[nosep]
    \item Developed a real-time multiplayer fighting game supporting 4 concurrent players.
    \item Implemented innovative rock-paper-scissors combat mechanics with weapon variety.
    \item Created powerup system and game balancing for competitive multiplayer experience.
\end{itemize}

\addvspace{\medskipamount} % Add vertical space between projects

% --- Project 4: Village Warriors ---
\textbf{Village Warriors} -- \href{https://assayyaad.itch.io/village-warriors}{Link (Clickable)} \hfill Unity, C\#, RPG Systems \hfill April 2021 \\
\textit{An RPG adventure game with a complex turn-based combat system}
\begin{itemize}[nosep]
    \item Designed and implemented comprehensive RPG mechanics including character progression and inventory systems.
    \item Created sophisticated turn-based combat system with strategic depth and variety.
    \item Developed game narrative and quest system for immersive player experience.
\end{itemize}

\addvspace{\medskipamount} % Add vertical space between projects

% --- Project 5: Tool Visualization in Phaser ---
\textbf{Tool Visualization in Phaser} -- \href{https://assayyaad.itch.io/anthima-phaser}{Link (Clickable)} \hfill JavaScript, Phaser, Web Development \hfill June 2024 \\
\textit{Tool Visualization in Phaser is a project aimed at visualizing and developing game systems using the Phaser framework.}
\begin{itemize}[nosep]
    \item Developed interactive web-based game system visualizations using Phaser framework.
    \item Created educational tools for understanding game development concepts and architectures.
    \item Implemented real-time system demonstrations for learning and prototyping purposes.
\end{itemize}

\addvspace{\medskipamount} % Add vertical space between projects

% --- Project 6: TicTacToe With Odin & SDL2 ---
\textbf{TicTacToe With Odin \& SDL2} -- \href{https://assayyaad.itch.io/xo}{Link (Clickable)} \hfill Odin, SDL2, Low-level Programming \hfill February 2025 \\
\textit{A simple Tic Tac Toe game developed using Odin and SDL2}
\begin{itemize}[nosep]
    \item Explored modern systems programming language Odin for game development.
    \item Implemented direct SDL2 integration for graphics and input handling.
    \item Created clean, efficient code demonstrating low-level game programming concepts.
\end{itemize}

\addvspace{\medskipamount} % Add vertical space between projects

% --- Project 7: Grid Horror ---
\textbf{Grid Horror} -- \href{https://assayyaad.itch.io/grid-horror}{Link (Clickable)} \hfill Procedural Generation, Game Design \hfill February 2025 \\
\textit{A simple horror game with a procedurally generated grid map}
\begin{itemize}[nosep]
    \item Developed atmospheric horror game with focus on procedural content generation.
    \item Implemented grid-based map generation system for varied gameplay experiences.
    \item Created tension-building mechanics and horror game design elements.
\end{itemize}

\addvspace{\medskipamount} % Add vertical space between projects

% --- Project 8: Coin Effects Tools ---
\textbf{Coin Effects Tools} -- \href{https://assayyaad.itch.io/riyal-coin}{Link (Clickable)} \hfill Unity, Tool Development \hfill March 2025 \\
\textit{A set of tools for creating coin effects in games}
\begin{itemize}[nosep]
    \item Developed specialized tools for creating appealing coin collection and currency effects.
    \item Created reusable components for common game monetization and reward systems.
    \item Focused on performance optimization for mobile and web game deployment.
\end{itemize}

% --- Certifications ---
\sectionheading{Certifications}

\textbf{FreeCodeCamp:}
\begin{itemize}[nosep]
    \item \textbf{JavaScript Algorithms and Data Structures} -- \href{https://freecodecamp.org/certification/Assayyaad/javascript-algorithms-and-data-structures}{Link (Clickable)}
\end{itemize}

\addvspace{\smallskipamount} % Small space between subsections

\textbf{Sololearn:}
\begin{itemize}[nosep]
    \item \textbf{Introduction to C\#} -- Certificate ID: CC-KQMDTAMA -- \href{https://www.sololearn.com/en/certificates/CC-KQMDTAMA}{Link (Clickable)}
    \item \textbf{Introduction to JavaScript} -- Certificate ID: CC-7A1QGUWT -- \href{https://www.sololearn.com/en/certificates/CC-7A1QGUWT}{Link (Clickable)}
    \item \textbf{Introduction to C++} -- Certificate ID: CT-DKF29HTQ -- \href{https://www.sololearn.com/en/certificates/CT-DKF29HTQ}{Link (Clickable)}
    \item \textbf{Tech for Everyone} -- Certificate ID: CC-49YAACNH -- \href{https://www.sololearn.com/en/certificates/CC-49YAACNH}{Link (Clickable)}
\end{itemize}

% --- Languages ---
\sectionheading{Languages}
\textbf{Arabic}: Native \\
\textbf{English}: Fluent \\
\textbf{Japanese}: Basic

% --- Interests ---
\sectionheading{Interests}
\textbf{eSports} -- Following competitive gaming scenes and tournaments \\
\textbf{Gaming} -- Passionate about playing and analyzing game mechanics and design \\
\textbf{Anime} -- Explores the storytelling and visual styles of anime \\
\textbf{Open Source} -- Contributing to and maintaining open source projects \\
\textbf{Paper Craft} -- Calms the mind with building physical models \\

% --- Online Presence ---
\sectionheading{Online Presence}
\textbf{Portfolio \& Games:} \href{https://assayyaad.itch.io}{itch.io (Clickable)} \\
\textbf{Development Activity:} \href{https://wakatime.com/@Assayyaad}{Wakatime (Clickable)} \\
\textbf{Game Jams:} \href{https://globalgamejam.org/users/assayyaad}{Global Game Jam (Clickable)} \\
\textbf{Learning Platforms:} \href{https://www.sololearn.com/en/profile/17032869}{Sololearn (Clickable)}, \href{https://www.freecodecamp.org/Assayyaad}{FreeCodeCamp (Clickable)}, \href{https://www.codecademy.com/profiles/Assayyaad}{Codecademy (Clickable)}, \href{https://exercism.org/profiles/Assayyaad}{Exercism (Clickable)} \\
\textbf{Social:} Discord -- @Assayyaad, \href{https://x.com/Assayyaad}{X/Twitter (Clickable)}, \href{https://linkedin.com/in/Assayyaad}{LinkedIn (Clickable)}, \href{https://youtube.com/@Assayyaad}{YouTube (Clickable)}

% --- DOCUMENT END ---
\end{document}